---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(magrittr)
library(glue)
library(reshape2)
```

```{r}
library(rvest)
library(xml2)
```

First, I would like to see the cost of Living in Texas so I downloaded the data from the website. I then briefly overviewed the cost of living in texas across different domains: 
```{r}
Texas <- read_html("https://www.bestplaces.net/cost_of_living/city/texas/austin")
cost <- html_nodes(Texas, "#mainContent_dgCostOfLiving td")
html_text(cost)
```

Next, I turned the html file into a data frame for exploration:
```{r}
Cost <- html_nodes(Texas, css = "table")
Cost_of_living <- html_table(Cost, header = TRUE, fill = TRUE)[[2]]
Cost_of_living
```

For ease of exploration and graphing, I decided to turn it into long format:
```{r}
Cost_long <- melt(Cost_of_living, id.vars=c("COST OF LIVING"))
colnames(Cost_long)[1] <- "Living"
colnames(Cost_long)[3] <- "Cost"
Cost_long

```

Looking at the data frame, I realized the cost values of United States are consistently the same across different domains so instead of graphing values of United States, I put them as a reference line.
```{r}
Cost_long %>%
	filter(variable != "United States") %>%
	ggplot(aes(x=Living, y=Cost, fill = Living)) +
    geom_bar(stat = "identity") + 
	  geom_hline(yintercept = 100, colour = "red", linetype = "dashed", size = 1) + 
	  annotate("text",x = 1.5, y=105,size=3,label=c("United States (Reference Line)")) + 
	  theme_bw() + 
	  xlab("Living Indices") + ylab("Cost") +
	  ggtitle("Cost of Living in Austin, Texas compared to United States")
```

Next, I explored the Education aspect of Texas, then turned them into dataframe: 
```{r}
Texas_education <- read_html("https://www.bestplaces.net/education/city/texas/austin")
Education <- html_table(Texas_education, header = TRUE, fil = TRUE)[[2]]
Education
```

Looking at the dataframe, I realized that the education measurement units are not the same. The first 3 aspects are related to cost of Education, whereas the last 3 aspects are related to ratio between students and staff/teacher. 

Thus, I divided the dataframe into 2 parts. The first part explored the cost of education:
```{r}
Education_Cost <- c("Expend. per Student", "Educ. Expend. per Student", "Instr. Expend. per Student")
Cost_Education <- Education[Education$EDUCATION %in% Education_Cost, ] %>%
	melt(id.vars = c("EDUCATION")) %>%
	mutate(value = value %>%
				 	str_replace_all("\\D","") %>%
				 	as.numeric())
Cost_Education
```

graph of cost of education:
```{r}
ggplot(data=Cost_Education, aes(x=EDUCATION, y=value, fill=variable)) + 
    geom_bar(colour="black", stat="identity",
             position=position_dodge(),
             size=.3) +                        
    scale_fill_hue(name="States") +      
    xlab("Education Indices") + ylab("COST") +
    ggtitle("Education Cost In Austin, Texas Compared to United States") +   
    theme_bw()
```

The second part explored the ratio between students and staff/teachers:
```{r}
Education_Ratio <- c("Pupil/Teacher Ratio", "Students per Librarian", "Students per Counselor")

Ratio_Education <- Education[Education$EDUCATION %in% Education_Ratio, ] %>%
	melt(id.vars = c("EDUCATION")) %>%
  mutate(value = value %>%
  			 as.numeric())
Ratio_Education
```

graph of ratio education:
```{r}
ggplot(data=Ratio_Education, aes(x=EDUCATION, y=value, fill=variable)) + 
    geom_bar(colour="black", stat="identity",
             position=position_dodge(),
             size=.3) +                        
    scale_fill_hue(name="States") +      
    xlab("Education Indices") + ylab("Ratio") +
    ggtitle("Education Ratio In Austin, Texas Compared to United States") +   
    theme_bw()
```

